\section{Work Experience}
  \resumeSubHeadingListStart
  
   \resumeSubheadingWork
      {Senior System Reliability Engineer}{Oct. 2023 -- Present}
      {CyberCX}{Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Developed standardized CI pipelines for Python projects, improving deployment efficiency in a secure, off-internet environment.}
        \resumeItem{Led monitoring and alerting with a Python-based application, integrating InfluxDB, Elasticsearch, Grafana, and Telegraf for real-time system insights.}
        \resumeItem{Implemented and maintained secure, self-hosted CI/CD processes, enhancing system reliability and cybersecurity resilience.}
      \resumeItemListEnd

    \resumeSubheadingWork
      {Site Reliability Engineer}{Feb. 2022 -- Oct. 2023}
      {Qantas}{Sydney, NSW}
      \resumeItemListStart
      \resumeItem{Optimized AWS ECS microservices for peak performance, employing Docker, Kubernetes, and conducting incident management with a 24x7 PagerDuty on-call system.}
      \resumeItem{Managed comprehensive monitoring using Splunk, Cloudwatch, Datadog, Grafana, and Prometheus; streamlined deployments with Jenkins, Ansible, and Terraform.}
      \resumeItem{Led Java Spring Boot service lifecycle on GitHub, from design to refinement, enhancing quality with SonarQube and facilitating collaboration through Slack, JIRA, and Confluence.}
      \resumeItemListEnd

    \resumeSubheadingWork
      {Software Engineer}{Sept. 2020 -- Feb. 2022}
      {SICE}{Sydney, NSW}
      \resumeItemListStart
      \resumeItem{Implemented and tested software for operations control with Agile methodologies.}
      \resumeItem{Enhanced regulated project documentation for precision and compliance.}
      \resumeItem{Leveraged Python and Ansible for DevOps automation and scripting.}
      \resumeItemListEnd

    \resumeSubheadingWork
      {Information Technologist}{May 2018 -- March 2020}
      {A\&M Digital Initiatives}{College Station, Texas}
      \resumeItemListStart
      \resumeItem{Managed IT support and streamlined ticketing workflow; introduced automation for efficient maintenance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
